\section{Banville}

Generally speaking, SunDog is a non-linear game which allows a player
to explore its universe any way they choose.  There is, however, an
end-game objective, which is to fulfill the contract that Zed's uncle
had taken to complete the colony of Banville.

The contract requires the delivery of a number of goods in phases (nine
in total) to a depot in Banville.  Each phase has a shopping list of
specific goods that will need to be purchased and delivered.  The
colony also requires the delivery of cryogens which have been left in
different depots of various planets that need to be collected in order
to complete the phase.  Once all of the required items have been collected,
the next phase will begin and the colony's map size will increase.


\begin{enumerate}
 \item Phase 1
 \begin{itemize}
  \item Fruits \slash Vegetables
  \item Grains \slash Cereals
  \item Seeds \slash Sprouts
  \item Stock Embryos
  \item Bulk Plastics
 \end{itemize}

 \item Phase 2
 \begin{itemize}
  \item Meats
  \item Spices \slash Herbs
  \item Sunsuns
  \item Wood \slash Fibers
  \item Bulk Metals
  \item Cryogens x 2
 \end{itemize}

 \item Phase 3
 \begin{itemize}
  \item Food
  \item Comgear
  \item Synthesizers
  \item Computers
  \item Bulk Textiles
  \item Cryogens x 4
 \end{itemize}

 \item Phase 4
 \begin{itemize}
  \item Cadcams
  \item Bulk Synthetics
  \item Grains \slash Cereals
  \item Nullgravs
  \item Silichips
  \item Spices \slash Herbs
  \item Cryogens
 \end{itemize}

 \item Phase 5
 \begin{itemize}
  \item Clothing
  \item Droids
  \item Fruits \slash Vegetables
  \item Meats
  \item Pharmaceuticals
  \item Cryogens x 2
 \end{itemize}

 \item Phase 6
 \begin{itemize}
  \item Gold
  \item Hand Weapons
  \item Silichips
  \item Sunsuns
  \item Solar Cells
  \item Cryogens x 3
 \end{itemize}

 \item Phase 7
 \begin{itemize}
  \item Biochips
  \item Fruits \slash Vegetables
  \item Gems \slash Crystals
  \item Organics
  \item Silichips
  \item Stimulants
  \item Polyglass
  \item Cryogens x 2
 \end{itemize}

 \item Phase 8
 \begin{itemize}
  \item Clothing
  \item Biochips
  \item Pharmaceuticals
  \item Radioactives
  \item Rare Earths
  \item Synthetic Stem Cells
  \item Synthesizers
  \item Medical Equipment
  \item Cryogens x 2
 \end{itemize}

 \item Phase 9
 \begin{itemize}
  \item Robotics
  \item Antimatter
  \item Art Objects
  \item Centrifuges
  \item Droids
  \item Exotic Metals
  \item Furs \slash Silks
  \item Radioactives
  \item Cryogens
 \end{itemize}
\end{enumerate}

Open Items:
\begin{itemize}
\item Where does the player buy the booster?  In a bar or in the equipment
shop?
\item When is the booster available?  After Phase 8?
\end{itemize}
